---
title: "WordCloud"
author: "JeffreyChen"
date: "2018/3/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Rfacebook)

library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)

token  = "EAACEdEose0cBAPvEDY17XqX8qxLlkXKkBEbNRkkiBZAomonHZBrvJ0x1HTKshpYJeP4Vw2uc0GiZBJDjZB1jCpdK5CLOqYadnOpOGn788YZCk4xtagqHJCdsM9G3wCND6YtZB6o2rcFZCo95sNg8ebMlXGiMswQqmFn2XjFAV9DnSWwjODEeX9t22wQgXc0HjpsTIlD3h1fiwZDZD"
page.id <- "5281959998"
page <- getPage(page.id, token, n = 200)
page$message[23] <- " "
posts <- page$message
posts <- gsub("[[:punct:]]", replacement = " ", posts)
posts <- gsub("\n", replacement = " ", posts)
head(posts)

docs <- Corpus(VectorSource(posts))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("the","The")) 
inspect(docs)

dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=150, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
